---
title: "Core Item Category Segmentation in Amazon Shopping Data"
output:
  html_document:
    df_print: paged
---


```{r}
library(stringr) 
library(splitstackshape)
library(igraph)
library(keyplayer)
library(devtools)
devtools::install_github("aslez/concoR")
library(concoR)
library(sna)
library(blockmodeling)
library(visNetwork)
library(tcltk)

```
#Caategory DAta
```{r}
con <- gzcon(url("http://snap.stanford.edu/data/bigdata/amazon/amazon-meta.txt.gz"))
tmp <- readLines(con)
tmp <- str_split_fixed(tmp,pattern=':', n=2)

#tmp <- readLines(con="D:/amazon-meta.txt")

tblcategories_count <- 1
tblcategories <- array('', dim=c(4000000,2))

tblMain_count <- 1
tblMain <- array('', dim=c(1000000,5))

```

#Clean and Organize Category Data

```{r}
rows <- nrow(tmp)
i <- 1
while (i <= rows) {

Id <- ''  
Id <- ifelse(tmp[i,1]=='Id',tmp[i,2] ,'') 
if (Id != ''){
  ASIN <- ifelse(tmp[i+1,1]=='ASIN',tmp[i+1,2],'') 
  title <- ifelse(tmp[i+2,1]== '  title',tmp[i+2,2],'') 
  group <- ifelse(tmp[i+3,1]== '  group',tmp[i+3,2],'') 
  salesrank <-  ifelse(tmp[i+4,1] == '  salesrank',tmp[i+4,2],'')
  #tblMain <- rbind(tblMain,data.frame(Id = Id, ASIN = ASIN, title = title, group = group, salesrank = salesrank))
  tblMain[tblMain_count,1] <- Id
  tblMain[tblMain_count,2] <- ASIN
  tblMain[tblMain_count,3] <- title
  tblMain[tblMain_count,4] <- group
  tblMain[tblMain_count,5] <- salesrank
  
  tblMain_count <- tblMain_count + 1
  

  
  j <- 0
  n <- as.integer(ifelse(tmp[i+6,1] == '  categories',tmp[i+6,2],''))
  n <- ifelse((is.na(n) || is.nan(n)),0,n)
  if (n > 0){ 
	tblcategories[tblcategories_count:(tblcategories_count+n-1),1] <- rep(Id,n)
	tblcategories[tblcategories_count:(tblcategories_count+n-1),2] <- tmp[(i+7):(i+6+n),1]
  }
  tblcategories_count <- tblcategories_count + n
  

  Id <- '' 
  
}

i = i +1
   
}

```

#Create Dataframe 

```{r}
rm(tmp)

tblMain <- tblMain[tblMain[,1]!='',]
#tblSimilar <- tblSimilar[tblSimilar[,1]!='',]
tblcategories <- tblcategories[tblcategories[,1]!='',]
#tblreviews <- tblreviews[tblreviews[,1]!='',]
  
tblMain2 <- data.frame(Id = as.numeric( tblMain[,1]), ASIN = tblMain[,2], title = tblMain[,3], group = tblMain[,4], salesrank = as.numeric(tblMain[,5]), stringsAsFactors = FALSE)
#tblSimilar2 <- data.frame(Id = as.numeric(tblSimilar[,1]), similar = tblSimilar[,2], stringsAsFactors = FALSE)  
tblcategories2 <- data.frame(Id = as.numeric(tblcategories[,1]), categories = tblcategories[,2], stringsAsFactors = FALSE) 
#tblreviews2 <- data.frame(Id = as.numeric(tblreviews[,1]), reviews = tblreviews[,2], stringsAsFactors = FALSE)

rm(tblMain) 
rm(tblcategories)

```
 
#Decomment one by one for Amazon data to extract

```{r}
con <- gzcon(url("http://snap.stanford.edu/data/amazon0302.txt.gz"))
#con <- gzcon(url("http://snap.stanford.edu/data/amazon0312.txt.gz"))
#con <- gzcon(url("http://snap.stanford.edu/data/amazon0505.txt.gz"))
#con <- gzcon(url("http://snap.stanford.edu/data/amazon0601.txt.gz"))
```

```{r}
x <- readLines(con)
x <- unlist(strsplit(x[5:length(x)], split="\t"))
x <- data.frame(from = x[seq(length(x)) %% 2 == 1], to = x[seq(length(x)) %% 2 != 1])
```

```{r}
names(tblMain2)[1]<-paste("from")
x <- merge(x, tblMain2, by="from", all.x=TRUE)
names(tblMain2)[1]<-paste("to")
x <- merge(x, tblMain2, by="to", all.x=TRUE)

tblcategories2 <- cSplit(tblcategories2, "categories","|")

names(tblcategories2)[1]<-paste("from")
x <- merge(x, unique(tblcategories2[,c('from','categories_04')]), by="from", all.x=TRUE)
names(tblcategories2)[1]<-paste("to")
x <- merge(x, unique(tblcategories2[,c('to','categories_04')]), by="to", all.x=TRUE)
x$count <- 1

rm(tblMain2) 
rm(tblcategories2)

```

#Aggregate Category Level 4

```{r}
x_sum <-aggregate(x$count, by=list(x$categories_04.x,x$categories_04.y,x$group.x,x$group.y),FUN=sum, na.rm=TRUE)
colnames(x_sum) <- c('from', 'to', 'fromGroup4','toGroup4','count')
net_all <- graph_from_data_frame(d=x_sum,directed=T)

x_sum_agg <- aggregate(x_sum$count, by=list(x_sum$from),FUN=sum, na.rm=TRUE)
x_sum_agg <- x_sum_agg[order(-x_sum_agg$x),]

```

#Raw data network

```{r}
#iso <- V(net)[degree(net)==0]
#net <- delete.vertices(net, iso)
plot(simplify(net_all),  vertex.size=7, vertex.label.cex=0.7, vertex.label.color="black", , edge.arrow.size=.3)
```

#Find Core Category Item upto complete all categories
#Compact Data

```{r}
#length(x_sum_agg$Group.1)
for (i in 1:50) { 
	net <- graph_from_data_frame(d=x_sum[x_sum$from %in% x_sum_agg$Group.1[1:i],],directed=T)       
	#print(length(V(net)))
	#print(x_sum_agg$Group.1[i])   
	if (length(V(net)) == length(x_sum_agg$Group.1)) break    
 }  

net <- simplify(net)

```

#Plot compact data network

```{r}
plot(net,  vertex.size=7, vertex.label.cex=0.7, vertex.label.color="black", , edge.arrow.size=.3)
 
```

#Statistics for raw data

```{r}
size <- length(V(simplify(net_all)))
average_distance <- mean_distance(simplify(net_all))
diameter <- diameter(simplify(net_all))
degree_centralization <- centralization.degree(simplify(net_all))$centralization
closeness_centralization <- centralization.closeness(simplify(net_all))$centralization
betweenness_centralization <- centralization.betweenness(simplify(net_all))$centralization
degree_centralization_sd <- sd(centralization.degree(simplify(net_all))$res)
closeness_centralization_sd <- sd(centralization.closeness(simplify(net_all))$res)
betweenness_centralization_sd <- sd(centralization.betweenness(simplify(net_all))$res)
density <- edge_density(simplify(net_all), loops=F)
average_degree <- mean(degree(as.matrix(as_adjacency_matrix(  simplify(net_all)))))
cohesion <- cohesion(simplify(net_all))
global_clustering_coefficient <- transitivity(simplify(net_all),type = 'global')
compactness <- mean(closeness(as.matrix(as_adjacency_matrix(  simplify(net_all)))))
mean_core <- mean(graph.coreness(simplify(net_all)))
median_core <- median(graph.coreness(simplify(net_all)))


table <- matrix(c(round(size,2), round(average_distance,2), round(diameter,2), round(degree_centralization,2), round(closeness_centralization,2), round(betweenness_centralization,2), round(degree_centralization_sd,2), round(closeness_centralization_sd,2), round(betweenness_centralization_sd,2),  round(density,2), round(average_degree,2), round(cohesion,2), round(compactness,2), round(global_clustering_coefficient,2), round(mean_core,2), round(median_core,2)))

rownames(table) <- c('size', 'Distance', 'Diameter', 'degree centralization', 'closeness centralization', 'betweenness centralization', 'degree centralization sd', 'closeness centralization sd', 'betweenness centralization sd', 'Density', 'Average Degree', 'Cohesion', 'Compactness', 'Global Clustering Coefficient', 'Mean Core', 'Median Core')

as.table(table)

```

#Build CORE subgroup

```{r}
x_sum2 <- as_adjacency_matrix(net)
x_sum2 <- as.matrix( x_sum2)
diag(x_sum2) <- 1
x_sum2.blks <- concor_hca(list(x_sum2), , max.iter = 300, p = 3)
#x_sum2.blks
```

```{r}
plot(net, vertex.color=x_sum2.blks$block, vertex.size=10, vertex.label.cex=0.8, vertex.label.color="black", edge.arrow.size=.3)

```

```{r}
x_sum2.mod <- blockmodel(x_sum2,x_sum2.blks$block )
#x_sum2.mod 
#1 is boss center core 

```

#Removing Core Category Group

```{r}
plot(induced_subgraph(simplify(net_all), c(x_sum2.mod$order.vector[x_sum2.mod$block.membership !=1] )), vertex.size=15, vertex.label.cex=0.8, vertex.label.color="black", edge.arrow.size=.3)

```

```{r}
x_sum2.reduced <- graph_from_adjacency_matrix(x_sum2.mod$block.model, weighted = TRUE, mode = "undirected")
```

#Block Group

```{r}
plot(simplify(x_sum2.reduced), vertex.size=50/unlist(x_sum2.reduced[[1]])[2:9]  )

```

#COre Group Network Stats

```{r}
net2 <- induced_subgraph(net_all, c(x_sum2.mod$order.vector[x_sum2.mod$block.membership ==1] ))
net2 <- simplify(net2)
size <- length(V(net2))
average_distance <- mean_distance(net2)
diameter <- diameter(net2)
degree_centralization <- centralization.degree(net2)$centralization
closeness_centralization <- centralization.closeness(net2)$centralization
betweenness_centralization <- centralization.betweenness(net2)$centralization
degree_centralization_sd <- sd(centralization.degree(net2)$res)
closeness_centralization_sd <- sd(centralization.closeness(net2)$res)
betweenness_centralization_sd <- sd(centralization.betweenness(net2)$res)
density <- edge_density(net2, loops=F)
average_degree <- mean(degree(as.matrix(as_adjacency_matrix(  net2))))
cohesion <- cohesion(net2)
global_clustering_coefficient <- transitivity(net2,type = 'global')
compactness <- mean(closeness(as.matrix(as_adjacency_matrix(  net2))))
mean_core <- mean(graph.coreness(net2))
median_core <- median(graph.coreness(net2))
table <- matrix(c(round(size,2),round(average_distance,2),round(diameter,2),round(degree_centralization,2),round(closeness_centralization,2),round(betweenness_centralization,2),round(degree_centralization_sd,2),round(closeness_centralization_sd,2),round(betweenness_centralization_sd,2),round(density,2),round(average_degree,2),round(cohesion,2),round(compactness,2),round(global_clustering_coefficient,2), round(mean_core,2), round(median_core,2)))
rownames(table) <- c('size','Distance','Diameter','degree centralization','closeness centralization','betweenness centralization','degree centralization sd','closeness centralization sd','betweenness centralization sd','Density','Average Degree','Cohesion', 'Compactness','Global Clustering Coefficient','Mean Core', 'Median Core')
as.table(table)


```

#Interaction chart for core item group

```{r}
nodes <- as_data_frame(net)
links <- data.frame(id = x_sum2.blks$vertex, block = x_sum2.blks$block)

network2 <- visNetwork(links,nodes  )  %>% visOptions(highlightNearest = TRUE, selectedBy= "block")
network2
```
```{r}

```

